\Title

### 2020-11-30 manuscript/manuscript.tex
Continue writing manuscript

>>>>

\subsection{Window size}

One factor that plays an important role on the gradient boosted equivalent
layers is the size of the overlapping windows used to create each set of
equivalent sources.
Smaller windows will reduce the amount of computer memory needed to fit the
source coefficients: smaller windows will reduce the size of Jacobian matrices
$\tilde{\mathbf{A}_k}$.
Nevertheless, the usage of smaller windows may produce less accurate
predictions: the equivalent sources cannot achieve the global minimum of the
misfit $\varphi(\mathbf{c})$ of equation~\ref{eq:misfit-unscaled}.
Moreover, the size of the overlapping windows might also impact on the
computation time needed to fit the source coefficients: smaller windows will
generate simpler least-square problems which are easier to solve, but they will
also create more iterations.

We want to assess how the size of the overlapping windows impacts both the
accuracy of the predictions and the computation time needed to fit the source
coefficients in comparison with the performance of the non-boosted equivalent
sources.
